A fast algorithm for finding efficient decisions in multi-objective problems with black-box multiextremal functions

### 2022-01-11 2022/OM&S/paper.tex
add one reference

For estimating the effectiveness of solving the test MCO problem the hypervolume (HV) index  \cite{} was used as the quality criterion of the Pareto set approximations built by the methods. Moreover, besides comparing the efficiency of tested algorithms via their HVs, an ``ideal'' value of HV was computed by means of selection of non-dominated nodes of a dense uniform grid placed in the feasible domain.

@@

During all experiments the method ALR was used with parameters $r=5.6$, $\sigma = 15$, $T=3$. Accuracy $\varepsilon$ from the stopping condition (\ref{eq:23}) was $0.05$ in bi-criteria problems and $0.01$ in 4-criteria ones.

>>>>

For estimating the effectiveness of solving the test MCO problem the hypervolume (HV) index  \cite{Evtushenko2014} was used as the quality criterion of the Pareto set approximations built by the methods. Moreover, besides comparing the efficiency of tested algorithms via their HVs, an ``ideal'' value of HV was computed by means of selection of non-dominated nodes of a dense uniform grid placed in the feasible domain.

@@

During all experiments the method ALR was used with parameters $r=5.6$, $\sigma = 18$, $T=3$. 
\textcolor[rgb]{1,0.41,0.13}{The use of $T=3$ corresponds to alternation of one ``local'' iteration and two ``global'' iterations.}
Accuracy $\varepsilon$ from the stopping condition (\ref{eq:23}) was $0.05$ in bi-criteria problems and $0.01$ in 4-criteria ones.
